---
title: "AirPassengers Transformation"
author: "Edimilson Torres de Oliveira Neto"
date: "2023-10-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Air Passengers Transformation

The Air Passengers Dataset is a built-in R dataset that contains Monthly totals of international airline passengers, from 1949 to 1960, in thousands.

The Air Passengers data is originally provided in a Time Series format.

```{r AirPassengers_Original}
AirPassengers
```
The data_transform function transforms the data into a tidy DataFrame with the columns Year, Month and Passengers

```{r AirPassengers_Transformation}
#Assigning the data to a variable
data <- AirPassengers

#Importing the function from the R file of the repository
source("transform_data.R")

#Printing the transformed data
print(head(data_transform(data)))

```
The data_transform function has two arguments "data" and "by_year". The first one provides the "AirPassengers" original dataset. The second parameter is optional and it has a default value of FALSE. In case the parameter is changed to TRUE, then the resulting dataset will be presented grouped by Year.

```{r AirPassengers_by_year}
#Printing the transformed data grouped by year
print(head(data_transform(data, by_year = TRUE)))

```
